Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-27 writing/DraftExposurePaper/DraftExposurePaper.Rmd
work on loop to ID station number

```{r}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
#alex_weather <- weather_fips(fips = alex_fips,
                             #date_min = "2010-06-25",
                             #date_max = "2010-07-02",
                             #var = "PRCP") # Returns warning: "sorry, no data found"
                                            # and problemin station_ids$meta . . .
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
#ike_weather <- county_timeseries(fips = ike_fips,
                                 #date_min = "2008-09-01",
                                 #date_max = "2008-09-14",
                                 #out_directory = paste0("/Users/joshuaferreri",
                                                # "/Documents/ike_timeseries"),
                                 #out_type = ".csv")
ike_weather <- weather_fips(fips = ike_fips[1],
                             date_min = "2008-09-01",
                             date_max = "2010-09-14",
                             var = "PRCP") # Same thing here
```

>>>>

```{r}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
#alex_weather <- weather_fips(fips = alex_fips,
                             #date_min = "2010-06-25",
                             #date_max = "2010-07-02",
                             #var = "PRCP") # Returns warning: "sorry, no data found"
                                            # and problemin station_ids$meta . . .
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
#ike_weather <- county_timeseries(fips = ike_fips,
                                 #date_min = "2008-09-01",
                                 #date_max = "2008-09-14",
                                 #out_directory = paste0("/Users/joshuaferreri",
                                                # "/Documents/ike_timeseries"),
                                 #out_type = ".csv")
ike_weather <- weather_fips(fips = ike_fips[1],
                             date_min = "2008-09-01",
                             date_max = "2008-09-14",
                             var = "PRCP") 
```

Trying to create a loop to identify the FIPS codes with the greatest number of stations reporting for each time period.

```{r}
test <- data.frame(fips = ike_fips[1:2], station = NA)
#for(fips in ike_fips[1:2]){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        test[fips, "stations"] <- max(ike_weather$daily_weather$prcp_reporting)
} #Still working on it
ike_table <- data.frame(fips = ike_fips, station = NA)
#for(fips in ike_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ , "station"] <- max(ike_weather$daily_weather$prcp_reporting)
} #still working on it
```
